```{r, include=FALSE}
require(ggplot2)
require(scales)

knitr::opts_chunk$set(fig.path='../doc/images/')
knitr::opts_chunk$set(out.width = '400px')
knitr::opts_chunk$set(dpi=200)
```

# The Kolmogorov Smirnov Test

```{r load, echo=FALSE}
critical_values <- read.table("critical_values.tsv", sep="\t", header=TRUE)
colnames(critical_values) <- c("n1", "n2", "confidence", "numerical_recipes")
critical_values$confidence <- as.numeric(as.character(critical_values$confidence))
critical_values$n1 <- as.numeric(as.character(critical_values$n1))
critical_values$n2 <- as.numeric(as.character(critical_values$n2))
critical_values$numerical_recipes <- as.numeric(as.character(critical_values$numerical_recipes))

critical_values <- critical_values[critical_values$confidence == 0.95,]

calculate_critical_value_soest_95 <- function(n1, n2) {  
  factor = (n1 + n2) / (n1 * n2);
  return (1.36 * sqrt(factor));
}

critical_values$soest <- calculate_critical_value_soest_95(
  critical_values$n1, critical_values$n2
)

normal01 <- read.table("normal_0_1.tsv", sep="\t", header=FALSE)
colnames(normal01) <- c("x")
normal01$ecdf <- ecdf(normal01$x)(normal01$x)

normal012 <- read.table("normal_0_1.2.tsv", sep="\t", header=FALSE)
colnames(normal012) <- c("x")
normal012$ecdf <- ecdf(normal012$x)(normal012$x)

normal014 <- read.table("normal_0_1.4.tsv", sep="\t", header=FALSE)
colnames(normal014) <- c("x")
normal014$ecdf <- ecdf(normal014$x)(normal014$x)

normal02 <- read.table("normal_0_2.tsv", sep="\t", header=FALSE)
colnames(normal02) <- c("x")
normal02$ecdf <- ecdf(normal02$x)(normal02$x)

normal021 <- read.table("normal_0_2.1.tsv", sep="\t", header=FALSE)
colnames(normal021) <- c("x")
normal021$ecdf <- ecdf(normal021$x)(normal021$x)

normal022 <- read.table("normal_0_2.2.tsv", sep="\t", header=FALSE)
colnames(normal022) <- c("x")
normal022$ecdf <- ecdf(normal022$x)(normal022$x)

normal023 <- read.table("normal_0_2.3.tsv", sep="\t", header=FALSE)
colnames(normal023) <- c("x")
normal023$ecdf <- ecdf(normal023$x)(normal023$x)

normal024 <- read.table("normal_0_2.4.tsv", sep="\t", header=FALSE)
colnames(normal024) <- c("x")
normal024$ecdf <- ecdf(normal024$x)(normal024$x)

normal11 <- read.table("normal_1_1.tsv", sep="\t", header=FALSE)
colnames(normal11) <- c("x")
normal11$ecdf <- ecdf(normal11$x)(normal11$x)

http <- read.table("http.tsv", sep="\t", header=TRUE)
colnames(http) <- c("ctime", "dtime", "ttime", "wait")
http$ctime <- as.numeric(as.character(http$ctime))
http$dtime <- as.numeric(as.character(http$dtime))
http$ttime <- as.numeric(as.character(http$ttime))
http$wait <- as.numeric(as.character(http$wait))
http$idx <- 1:nrow(http)
http$ttime_ecdf <- ecdf(http$ttime)(http$ttime)

http1 <- read.table("http.1.tsv", sep="\t", header=TRUE)
colnames(http1) <- c("ctime", "dtime", "ttime", "wait")
http1$ctime <- as.numeric(as.character(http1$ctime))
http1$dtime <- as.numeric(as.character(http1$dtime))
http1$ttime <- as.numeric(as.character(http1$ttime))
http1$wait <- as.numeric(as.character(http1$wait))
http1$idx <- 1:nrow(http1)
http1$ttime_ecdf <- ecdf(http1$ttime)(http1$ttime)

http2 <- read.table("http.2.tsv", sep="\t", header=TRUE)
colnames(http2) <- c("ctime", "dtime", "ttime", "wait")
http2$ctime <- as.numeric(as.character(http2$ctime))
http2$dtime <- as.numeric(as.character(http2$dtime))
http2$ttime <- as.numeric(as.character(http2$ttime))
http2$wait <- as.numeric(as.character(http2$wait))
http2$idx <- 1:nrow(http1)
http2$ttime_ecdf <- ecdf(http2$ttime)(http2$ttime)

http3 <- read.table("http.3.tsv", sep="\t", header=TRUE)
colnames(http3) <- c("ctime", "dtime", "ttime", "wait")
http3$ctime <- as.numeric(as.character(http3$ctime))
http3$dtime <- as.numeric(as.character(http3$dtime))
http3$ttime <- as.numeric(as.character(http3$ttime))
http3$wait <- as.numeric(as.character(http3$wait))
http3$idx <- 1:nrow(http1)
http3$ttime_ecdf <- ecdf(http3$ttime)(http3$ttime)

http4 <- read.table("http.4.tsv", sep="\t", header=TRUE)
colnames(http4) <- c("ctime", "dtime", "ttime", "wait")
http4$ctime <- as.numeric(as.character(http4$ctime))
http4$dtime <- as.numeric(as.character(http4$dtime))
http4$ttime <- as.numeric(as.character(http4$ttime))
http4$wait <- as.numeric(as.character(http4$wait))
http4$idx <- 1:nrow(http1)
http4$ttime_ecdf <- ecdf(http4$ttime)(http4$ttime)

twtr <- read.table("twtr.tsv", sep="\t", header=TRUE)
twtr$open_ecdf <- ecdf(twtr$open)(twtr$open)
twtr$volume_ecdf <- ecdf(twtr$volume)(twtr$volume)
```

## Critical Values Plot

```{r critical-values, echo=FALSE}
ggplot(critical_values, aes(x=n2, y=soest)) +
  geom_line(alpha=0.5, size=1) +
  geom_line(alpha=0.5, size=1, aes(x=n2, y=numerical_recipes)) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## N(0,1), N(0,2) Empirical Cumulative Distribution Function

```{r n01n02ecdf, echo=FALSE}
ggplot(normal01, aes(x=x, y=ecdf)) +
  geom_line(alpha=0.5, size=1) +
  geom_line(data=normal02, alpha=0.5, size=1) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## N(0,1), N(1,1) Empirical Cumulative Distribution Function

```{r n01n11ecdf, echo=FALSE}
ggplot(normal01, aes(x=x, y=ecdf)) +
  geom_line(alpha=0.5, size=1) +
  geom_line(data=normal11, alpha=0.5, size=1) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## N(0,1) Density

```{r n01, echo=FALSE, }
ggplot(normal01, aes(x=x)) +
  stat_density(alpha=0.5, colour="black") +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## N(0,2) Density

```{r n02, echo=FALSE}
ggplot(normal02, aes(x=x)) +
  stat_density(alpha=0.5, colour="black") +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## N(1,1) Density

```{r n11, echo=FALSE}
ggplot(normal11, aes(x=x)) +
  stat_density(alpha=0.5, colour="black") +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## N(0,1), N(0,2), N(1,1) Density

```{r n01n02n11, echo=FALSE}
ggplot(normal01, aes(x=x)) +
  stat_density(alpha=0.5, colour="mistyrose4", fill="mistyrose4") +
  stat_density(data=normal02, alpha=0.5, colour="black") +
  stat_density(data=normal11, alpha=0.5, colour="slateblue4", fill="slateblue4") +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## N(0,2)-1 Density

```{r n021, echo=FALSE}
ggplot(normal021, aes(x=x)) +
  stat_density(alpha=0.5, colour="black") +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## N(0,2), N(0,2)-1 Density

```{r n02n021, echo=FALSE}
ggplot(normal02, aes(x=x)) +
  stat_density(alpha=0.5, colour="mistyrose4", fill="mistyrose4") +
  stat_density(data=normal021, alpha=0.5, colour="slateblue4", fill="slateblue4") +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## N(0,2), N(0,2)-1 Empirical Cumulative Distribution Function

```{r n02n021ecdf, echo=FALSE}
ggplot(normal02, aes(x=x, y=ecdf)) +
  geom_line(alpha=0.5, size=1) +
  geom_line(data=normal021, alpha=0.5, size=1) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## N(0,2), N(0,2)-2 Empirical Cumulative Distribution Function

```{r n02n022ecdf, echo=FALSE}
ggplot(normal02, aes(x=x, y=ecdf)) +
  geom_line(alpha=0.5, size=1) +
  geom_line(data=normal022, alpha=0.5, size=1) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## N(0,2), N(0,2)-3 Empirical Cumulative Distribution Function

```{r n02n023ecdf, echo=FALSE}
ggplot(normal02, aes(x=x, y=ecdf)) +
  geom_line(alpha=0.5, size=1) +
  geom_line(data=normal023, alpha=0.5, size=1) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## N(0,2), N(0,2)-4 Empirical Cumulative Distribution Function

```{r n02n024ecdf, echo=FALSE}
ggplot(normal02, aes(x=x, y=ecdf)) +
  geom_line(alpha=0.5, size=1) +
  geom_line(data=normal024, alpha=0.5, size=1) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## N(0,1)-2, N(0,2)-2 Density

```{r n012n022, echo=FALSE}
ggplot(normal022, aes(x=x)) +
  stat_density(alpha=0.5, colour="slateblue4", fill="slateblue4") +
  stat_density(data=normal012, alpha=0.5, colour="mistyrose4", fill="mistyrose4") +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## N(0,1)-2, N(0,2)-2 Empirical Cumulative Distribution Function

```{r n012n022ecdf, echo=FALSE}
ggplot(normal022, aes(x=x, y=ecdf)) +
  geom_line(alpha=0.5, size=1) +
  geom_line(data=normal012, alpha=0.5, size=1) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## N(0,1)-4, N(0,2)-1 Density

```{r n014n021, echo=FALSE}
ggplot(normal021, aes(x=x)) +
  stat_density(alpha=0.5, colour="slateblue4", fill="slateblue4") +
  stat_density(data=normal014, alpha=0.5, colour="mistyrose4", fill="mistyrose4") +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## N(0,1)-4, N(0,2)-1 Empirical Cumulative Distribution Function

```{r n014n021ecdf, echo=FALSE}
ggplot(normal021, aes(x=x, y=ecdf)) +
  geom_line(alpha=0.5, size=1) +
  geom_line(data=normal014, alpha=0.5, size=1) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## HTTP Timeseries

```{r http-timeseries, echo=FALSE}
ggplot(http, aes(x=idx, y=ttime)) +
  geom_line(alpha=0.5) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## HTTP Density

```{r http-density, echo=FALSE}
ggplot(http, aes(x=ttime)) +
  stat_density(alpha=0.5, colour="black") +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## HTTP Empirical Cumulative Distribution Function

```{r http-ecdf, echo=FALSE, }
ggplot(http, aes(x=ttime, y=ttime_ecdf)) +
  geom_line(alpha=0.5, size=1) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## HTTP1 Timeseries

```{r http1-timeseries, echo=FALSE}
ggplot(http1, aes(x=idx, y=ttime)) +
  geom_line(alpha=0.5) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## HTTP1 Density

```{r http1-density, echo=FALSE}
ggplot(http1, aes(x=ttime)) +
  stat_density(alpha=0.5, colour="black") +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## HTTP2 Density

```{r http2-density, echo=FALSE}
ggplot(http2, aes(x=ttime)) +
  stat_density(alpha=0.5, colour="black") +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## HTTP3 Density

```{r http3-density, echo=FALSE}
ggplot(http3, aes(x=ttime)) +
  stat_density(alpha=0.5, colour="black") +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## HTTP4 Density

```{r http4-density, echo=FALSE}
ggplot(http4, aes(x=ttime)) +
  stat_density(alpha=0.5, colour="black") +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## HTTP, HTTP4 Empirical Cumulative Distribution Function

```{r httphttp4ecdf, echo=FALSE}
ggplot(http, aes(x=ttime, y=ttime_ecdf)) +
  geom_line(alpha=0.5, size=1) +
  geom_line(data=http4, alpha=0.5, size=1) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## HTTP1, HTTP4 Empirical Cumulative Distribution Function

```{r http1http4ecdf, echo=FALSE}
ggplot(http1, aes(x=ttime, y=ttime_ecdf)) +
  geom_line(alpha=0.5, size=1) +
  geom_line(data=http4, alpha=0.5, size=1) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## TWTR Opening Price Timeseries

```{r twtr-open-timeseries, echo=FALSE}
ggplot(twtr, aes(x=timestamp, y=open)) +
  geom_line(alpha=0.5) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## TWTR Opening Price Density

```{r twtr-open-density, echo=FALSE}
ggplot(twtr, aes(x=open)) +
  stat_density(alpha=0.5, colour="black") +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## TWTR Opening Price Empirical Cumulative Distribution Function

```{r twtr-open-ecdf, echo=FALSE, }
ggplot(twtr, aes(x=open, y=open_ecdf)) +
  geom_line(alpha=0.5, size=1) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## TWTR Volume Timeseries

```{r twtr-volume-timeseries, echo=FALSE}
ggplot(twtr, aes(x=timestamp, y=volume)) +
  geom_line(alpha=0.5) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```

## TWTR Volume Density

```{r twtr-volume-density, echo=FALSE}
ggplot(twtr, aes(x=volume)) +
  stat_density(alpha=0.5, colour="black") +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  # Thousands commas on x axis for large integer trading volumes values.
  scale_x_continuous(labels=comma) +
  scale_y_continuous(labels=comma)
```

## TWTR Volume Empirical Cumulative Distribution Function

```{r twtr-volume-ecdf, echo=FALSE, }
ggplot(twtr, aes(x=volume, y=volume_ecdf)) +
  geom_line(alpha=0.5, size=1) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_y_continuous(labels=comma)
```
